Versioned Queries over RDF Archives:\\All You Need is SPARQL?

### 2020-10-10 paper.tex
camera ready
Minor edit

\RequirePackage{amsmath}
\documentclass{llncs}
\usepackage[utf8]{inputenc}
\PassOptionsToPackage{table}{xcolor}
\pagestyle{headings}  % This option shows page numbers, it have to be removed in the final document.
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{scalerel}
\usepackage{comment}
\usepackage{framed}
\usepackage{listings}
\usepackage{mathtools}
%\usepackage{pifont}% http://ctan.org/pkg/pifont
%\usepackage{balance}
%\usepackage{stmaryrd}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage{url}
\usepackage{inconsolata}
\usepackage{etoolbox}

@@

\maketitle

@@

We now reflect back on our research questions: (Q1) In terms of indexing space and time, incremental builds with an initial base version (\cbpd) are best. (Q2) In general the uncompressed IC representation (\ic) offers the best query runtimes, but interval TB (\tb) is quite competitive, and even outperforms IC for delta-version queries. (Q3) Rather than there being an overall winner, we note a time--space tradeoff, where less compact representations have faster queries and more compact representations have slower queries. Interval TB (\tb) arguably strikes the best balance for space and time, though this may not hold with more versions, particularly in RDF achives where triples are often added or removed multiple times, as a quadratic number of intervals may need to be accessed.

>>>>

\RequirePackage{amsmath}
\documentclass[a4paper]{llncs}
\usepackage[utf8]{inputenc}
\PassOptionsToPackage{table}{xcolor}
\pagestyle{headings}  % This option shows page numbers, it have to be removed in the final document.
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{scalerel}
\usepackage{comment}
\usepackage{framed}
\usepackage{listings}
\usepackage{mathtools}
%\usepackage{pifont}% http://ctan.org/pkg/pifont
%\usepackage{balance}
%\usepackage{stmaryrd}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage{url}
\usepackage{inconsolata}
\usepackage{etoolbox}

\newcommand\copyrighttext{%
  \footnotesize Copyright © 2020 for this paper by its authors. Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0).}
\newcommand\copyrightnotice{%
\begin{tikzpicture}[remember picture,overlay]
\node[anchor=south,yshift=70pt,xshift=\marginparsep] at (current page.south) {{\parbox{\dimexpr\textwidth-\fboxsep-\fboxrule\relax}{\copyrighttext}}};
\end{tikzpicture}%
}

@@

\maketitle
\copyrightnotice

@@

We now reflect back on our research questions: (Q1) In terms of indexing space and time, incremental builds with an initial base version (\cbpd) are best. (Q2) In general the uncompressed IC representation (\ic) offers the best query runtimes, but interval TB (\tb) is quite competitive, and even outperforms IC for delta-version queries. (Q3) Rather than there being an overall winner, we note a time--space tradeoff, where less compact representations have faster queries and more compact representations have slower queries. Interval TB (\tb) arguably strikes the best balance for space and time, though this may not hold with more versions, particularly in RDF archives where triples are often added or removed multiple times, as a quadratic number of intervals may need to be accessed.
